Supplementary Material for ``Evaluating infectious disease forecasts with allocation scoring rules''

### 2023-12-06 alloscore_manuscript/supplement.rnw
more painfully obtained iteration details

We also want to be able to decribe what further ``post-processing'' steps are required to find a sufficiently good approximation
to a Bayes act within the set
$\undertilde{\bm{F}}^{-1}(I_{\overline{k}})$ where $I_{\overline{k}}$ is the terminal search interval for $\tau^{\star}$.

>>>>

We also want to be able to decribes what further ``post-processing'' steps are required to find an approximate Bayes act in the set
$\undertilde{\bm{F}}^{-1}(I_{\overline{k}})$ where $\overline{k}$ is the final iteration step index.
